\documentclass[]{CV}

\usepackage{amssymb}
\usepackage{outlines}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{lipsum}
%\usepackage{geometry}
%\geometry{a4paper, margin=1cm}
\usepackage{enumitem}
\setlist[itemize]{left=-4pt, itemsep=0.3em, topsep=0.2em}



\fullname{SEYED AMIR KASAEI}
\jobtitle{Research Assistant, RIML Lab \& MSc Student, Software Engineering, Sharif University of Technology}


\begin{document}
\resumeheader
{\googlescholar{mUVrJwYAAAAJ}}
{\linkedin{amirkasaei}}
{\email{a.kasaei@me.com}}
{\website{amirkasaei.com}}
{\github{amirkasaei}}
{}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-3mm}
\begin{section}{EDUCATION}
\vspace{-2mm}
\begin{multicols}{2}
\begin{itemize}
    \item \textbf{M.Sc. in Computer Engineering} \\
    Sharif University of Technology - (Sep 2023 -- Present) \\
    \textit{Focus: Compositional Generation in T2I Diffusion Models} \\
    Supervisor: \href{https://scholar.google.com/citations?user=pRyJ6FkAAAAJ}{Dr. M H Rohban} \\
    GPA: 18.54/20
\end{itemize}

\columnbreak

\begin{itemize}
    \item \textbf{B.Sc. in Computer Engineering} \\
    University of Guilan (Sep 2019 -- Aug 2023) \\
    \textit{Focus: Medical Image Analysis} \\
    Supervisor: \href{https://scholar.google.com/citations?user=Qh5IJ94AAAAJ}{Dr. S A Mirroshandel} \\
    GPA: 19.58/20 - \textit{Ranked 1st} 
\end{itemize}
\end{multicols}
\end{section}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-5mm}
\begin{section}{RESEARCH INTERESTS}
\begin{itemize}
\item Computer Vision, Compositional and Multimodal Learning across Vision and Language
\item Text-to-Image Generation and Diffusion Models
\item Visual Reasoning and Semantic Alignment in Cross-Modal Systems
\end{itemize}
\end{section}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{section}{PUBLICATIONS}
\begin{itemize}
\item \textbf{CARINOX: Inference-time Scaling with Category-Aware Reward-based Initial Noise Optimization and Exploration} \newline
\underline{Seyed Amir Kasaei}, Ali Aghayari, Arash Marioriyad, Niki Sepasian, Shayan Baghayi Nejad, MohammadAmin Fazli, Mahdieh Soleymani Baghshah, Mohammad Hossein Rohban \newline
TMLR 2026\newline
\href{https://arxiv.org/abs/2509.17458}{arxiv.org/abs/2509.17458}

\item \textbf{Weeding Out Bad Seeds: Noise-Robust Unlearning for Text-to-Image Diffusion Models} \newline
Arian Komaei Koma, \underline{Seyed Amir Kasaei}, Ali Aghayari, Aida Aryafar, Matin Ghiasi, Amirhossein Souri, Mohammad Mosayyebi, AmirMahdi Sadeghzadeh, Mohammad Hossein Rohban \newline
Under Review at NeurIPS 2026

\item \textbf{Evaluating the Evaluators: Metrics for Compositional Text-to-Image Generation} \newline
\underline{Seyed Amir Kasaei}, Ali Aghayari, Arash Marioriyad, Niki Sepasian, MohammadAmin Fazli, Mahdieh Soleymani Baghshah, Mohammad Hossein Rohban \newline
NeurIPS 2025 Workshop GenProCC \newline
\href{https://arxiv.org/abs/2509.21227}{arxiv.org/abs/2509.21227}

\item \textbf{Hidden Meanings in Plain Sight: RebusBench for Evaluating Cognitive Visual Reasoning} \newline
\underline{Seyed Amir Kasaei}, Arash Marioriyad, Mahbod Khaleti, MohammadAmin Fazli, Mahdieh Soleymani Baghshah, Mohammad Hossein Rohban \newline
ICLR 2026 Workshop: From Human Cognition to AI Reasoning (HCAIR) \newline
\href{https://arxiv.org/abs/2604.01764}{arxiv.org/abs/2604.01764}


\item \textbf{Erasure or Erosion? Evaluating Compositional Degradation in Unlearned Text-To-Image Diffusion Models} \newline
Arian Komaei Koma, \underline{Seyed Amir Kasaei}, Ali Aghayari, AmirMahdi Sadeghzadeh, Mohammad Hossein Rohban \newline
CVPR 2026 Workshop on Machine Unlearning for Computer Vision \newline
\href{https://arxiv.org/abs/2604.04575}{arxiv.org/abs/2604.04575}



% \item \textbf{Hallucination as an Upper Bound: A New Perspective on Text-to-Image Evaluation} \newline
% \underline{Seyed Amir Kasaei}, Mohammad Hossein Rohban \newline
% NeurIPS 2025 Workshop GenProCC \newline
% \href{https://arxiv.org/abs/2509.21257}{arxiv.org/abs/2509.21257}

\item \textbf{Erased but Exploitable: Black-box Embedding-Aware Prompting
Against Unlearned Text-to-Image Diffusion Models} \newline
Arian Komaei Koma, \underline{Seyed Amir Kasaei}, Amirhossein Arefzadeh,
Roham Izadidoost, AmirMahdi Sadeghzadeh, Mohammad Hossein Rohban \newline
Under Review at TMLR


\end{itemize}
\end{section}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{section}{EXPERIENCE}

\textbf{Research Assistantships}
\begin{itemize}
    \item \textit{RIML Lab, Sharif University of Technology} \hfill Sep 2023 -- Present \\
    Supervisor: \href{https://scholar.google.com/citations?user=pRyJ6FkAAAAJ}{Dr. Mohammad Hossein Rohban} \\
    Focus: Compositional Generation, T2I Diffusion Models, Visual Reasoning, Multimodal Models

    \item \textit{University of Guilan} \hfill Sep 2022 -- Aug 2023 \\
    Supervisor: \href{https://scholar.google.com/citations?user=Qh5IJ94AAAAJ}{Dr. Seyed Abolghasem Mirroshandel} \\
    Focus: Medical Image Analysis
\end{itemize}
% \pagebreak

\textbf{Teaching Assistantships (Sharif University of Technology)}
\begin{itemize}
    \item \textit{Data Mining} (Head TA) --- Instructor: \href{https://scholar.google.com/citations?user=veo-8swAAAAJ}{Dr. Mohammad Amin Fazli} \hfill Sep 2025 -- Jan 2026 \\
    \textit{Duties:} Led course coordination, quiz design, and grading; assisted with lectures, assignments, and student support.

    \item \textit{System 2 in AI} --- Instructors: \href{https://scholar.google.com/citations?user=pRyJ6FkAAAAJ}{Dr. Mohammad Hossein Rohban}, \href{https://scholar.google.com/citations?user=S1U0KlgAAAAJ}{Dr. Mahdieh Soleymani Baghshah} \hfill Feb 2025 -- Jun 2025 \\
    \textit{Topics:} Compositional Generation, Inference-time scaling, Test-time adaptation $\mid$ \textit{Duties:} Material prep and grading.

    \item \textit{Deep Learning} --- Instructor: \href{https://scholar.google.com/citations?user=S1U0KlgAAAAJ}{Dr. Mahdieh Soleymani Baghshah} \hfill Feb 2025 -- Jun 2025 \\
    \textit{Topics:} Generative Models, VAE, GAN, Diffusion $\mid$ \textit{Duties:} Quiz and exam design, and grading.

    \item \textit{Intelligent Analysis of Biomedical Images} --- Instructor: \href{https://scholar.google.com/citations?user=pRyJ6FkAAAAJ}{Dr. Mohammad Hossein Rohban} \hfill Sep 2024 -- Jan 2025 \\
    \textit{Topics:} Diffusion and Generative Models $\mid$ \textit{Duties:} Supported exercises, exam/quiz design, and grading.
\end{itemize}

% \begin{itemize}
%     \item \textit{Data Mining}, Sharif University of Technology \hfill Sep 2025 -- Jan 2026 \\
%     Head Teaching Assistant — Instructor: \href{https://scholar.google.com/citations?user=veo-8swAAAAJ}{Dr. Mohammad Amin Fazli} \\
%     Led course coordination, quiz design, and grading; assisted with lectures, assignments, and student support

%     \item \textit{System 2 in AI}, Sharif University of Technology \hfill Feb 2025 -- Jun 2025 \\
%     Instructors: \href{https://scholar.google.com/citations?user=pRyJ6FkAAAAJ}{Dr. Mohammad Hossein Rohban}, \href{https://scholar.google.com/citations?user=S1U0KlgAAAAJ}{Dr. Mahdieh Soleymani Baghshah} \\
%     Assisted with course material preparation and quiz grading \\
%     Focus areas: Compositional Generation, Inference-time scaling, Test-time adaptation

%     \item \textit{Deep Learning}, Sharif University of Technology \hfill Feb 2025 -- Jun 2025 \\
%     Instructor: \href{https://scholar.google.com/citations?user=S1U0KlgAAAAJ}{Dr. Mahdieh Soleymani Baghshah} \\
%     Contributed to quiz and exam design, and grading \\
%     Focus areas: Generative Models, VAE, GAN, Diffusion

%     \item \textit{Intelligent Analysis of Biomedical Images}, Sharif University of Technology \hfill Sep 2024 -- Jan 2025 \\
%     Instructor: \href{https://scholar.google.com/citations?user=pRyJ6FkAAAAJ}{Dr. Mohammad Hossein Rohban} \\
%     Supported exercises, exam and quiz design, and grading \\
%     Focus areas: Diffusion and Generative Models

%     % \item \textit{Artificial Intelligence and Expert Systems}, University of Guilan \hfill Sep 2022 -- Jan 2023 \\
%     % Instructor: \href{https://scholar.google.com/citations?user=6lTfb7IAAAAJ}{Dr. Yasaman Boreshban} \\
%     % Assisted with projects and problem-solving
% \end{itemize}

%\textbf{Work Experience}
%\begin{itemize}
%    \item \textit{IT Support Technician}, Guilan Soha Seir \hfill Sep 2019 -- Sep 2023 \\
%    Skills: Troubleshooting · Hardware · Software · Technical
%\end{itemize}

\end{section}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-4mm}
% \begin{section}{SELECTED ACCOMPLISHED PROJECTS { - (Other Projects on \href{https://github.com/amirkasaei}{Github})}}
% \begin{itemize}

% \item \textbf{CT-scan Image Segmentation using 3D-UNet} - \href{https://github.com/amirkasaei/CT-scan-Image-Segmentation-using-3D-UNet}{Github repository}
%    \begin{itemize}
%         \item 3D-UNet model is implemented to segment liver in CT-scan images and compared to 2D-UNet
%         \item Scikit-learn, Torch, Numpy, Matplotlib, OpenCV
%     \end{itemize}

% \item \textbf{Breast Tumor Classification using GNN} - \href{https://github.com/amirkasaei/Breast-Tumor-Classification-using-GNN}{Github repository}
%    \begin{itemize}
%         \item GNN model is implemented  to classify Breast Tumor on BRACS dataset
%         \item Histocartography, DGL, Torch Geometric, Torchvision, Scikit-learn, Torch, Numpy, Matplotlib, OpenCV, Pandas
%     \end{itemize}

% \item \textbf{MAML on Human Sperm Abnormality Detection} - \href{https://github.com/amirkasaei/Modified-Human-Sperm-Morphology-Analysis}{Github repository}
% \begin{itemize}
% \vspace{-2mm}
%      \item We used MAML model to detected human sperm abnormality on its head, vacoule, acrosome, and tail. \vspace{-2mm}
% 	\item In this project we used \textbf{Learn2learn, Scikit-learn, PyTorch, Numpy, Matplotlib, seaborn}.
% \end{itemize}
    
% \item \textbf{Arabic Broken Plurals} - \href{https://github.com/amirkasaei/Arabic-Broken-Plurals}{Github repository}
%    \begin{itemize}
%         \item We implemented a character based Machine Translation model to predict plural form of arabic words
%         \item BERT Embedding, Pandas, Scikit-learn, Keras, Tensorflow, Numpy
%         \item This project was done as a partnership with Dr. SA Mirroshandel for \textbf{Stony Brook University}
%     \end{itemize}
    
% %\item \textbf{Image Segementation on CamVid using SegNet} - \href{https://github.com/amirkasaei/Image-Segementation-CamVid-using-SegNet}{Github repository}
%   % \begin{itemize}
%   %      \item SegNet model is implemented to segment images on CamVid dataset
%     %    \item Pandas, Scikit-learn, Keras, Tensorflow, Numpy, Matplotlib
%    % \end{itemize}
    
%      \item \textbf{Multi-Class Weather Classification} - \href{https://github.com/amirkasaei/Multi-Class-Weather-Classification}{Github repository}
%    \begin{itemize}
%         \item Simple CNN, Resnet And Inception Net are all implemented an d compared for image classification
%         \item  Pandas, Scikit-learn, Keras, Tensorflow, Numpy, Matplotlib
%     \end{itemize}
    
% \pagebreak  
% \item \textbf{An Odd Music Generator} - \href{https://github.com/amirkasaei/An-Odd-Music-Generator}{Github repository}
%    \begin{itemize}
%         \item We implemented a Denoising Auto Encoder model to denoise the input song, a Deep Neural Network to recognize notes in the input song and a Language model to predict the next note of  the song.\vspace{-2mm}
%         \item Scikit-learn, Keras, Tensorflow, Numpy, Librosa, Matplotlib
%     \end{itemize} 
    
    
% %   \item \textbf{Multi-Lable Text Classification} - \href{https://github.com/amirkasaei/Multi-Lable-Text-Classification}{Github repository}
%   % \begin{itemize}
% %        \item We implemented a multi task language model to predict class type of subjects and also the sentimental analysis of sentences.\vspace{-2mm}
%    %     \item Pandas, Scikit-learn, Keras, Tensorflow, Numpy, Hazm, NLTK, Matplotlib
%    % \end{itemize}

% %\pagebreak

% \end{itemize}
% \end{section}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1mm}
\begin{section}{NOTABLE SELECTED COURSES}
\vspace{-2mm}
\begin{multicols}{2}
\textbf{Master of Science}
     \begin{itemize}
     \item Data Science in Software Engineering - 19 / 20
	\item Intelligent Analysis of Biomedical Images - 20 / 20
	\item Deep Learning - 16.7 / 20
	\item Algorithmic Game Theory - 19.5 / 20
	% \item Massive Data Algorithms - 19.5 / 20
	% \item Randomized Algorithms - 16.5 / 20
	% \item Software Engineering - 18.5 / 20
	\vfill
    \end{itemize}
	
    \columnbreak
\textbf{Bachelor of Science}
    \begin{itemize}
	\item Fundamental of Data Mining - 20 / 20
	\item Introduction to Deep Learning - 19.8 / 20
	\item Introduction to Machine Learning - 18.16 / 20
	\item Fundamental of Language and Speech Processing - 20 / 20
	% \item Artificial Intelligence and Expert Systems - 20 / 20
	
% 	%\item \textbf{Database} - 20 / 20
% 	%\item \textbf{Data Structures} - 20 / 20
% 	%\item \textbf{Software Testing} - 20 / 20
% 	%\item \textbf{Algorithm Design} - 20 / 20
% 	%\item \textbf{Principles of Compiler Design} - 20 / 20
% 	%\item \textbf{The Theory of Languages ​​and Automata} - 19.75 / 20
	
% 	%\item \textbf{Engineering Statistics and Probability} - 20 / 20
% 	\item Signals and Systems - 19.5 / 20
% 	\item Engineering Mathematics - 19.75 / 20


% 	\item Differential Equations - 18.75 / 20
% 	\item Discrete Mathematics - 19.75 / 20
	
    \end{itemize}
    \end{multicols}
\end{section}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-3mm}
\begin{section}{HONORS \& AWARDS}
\begin{itemize}
\item \textbf{Exceptional Talent Admission}, Sharif University of Technology \hfill Sep 2023
\newline Awarded direct admission to M.Sc. in Computer Engineering as an exceptional talented student.

\item \textbf{Ranked 1st}, B.Sc. Computer Engineering, University of Guilan \hfill 2019 -- 2023
\newline Highest GPA among all undergraduate Computer Engineering students.
\end{itemize}
\end{section}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{section}{SKILLS}
\begin{itemize}
    \item \textbf{Machine Learning \& Computer Vision:} Generative Models, Multi-modals, Diffusion, VLMs, Visual Reasoning
    \item \textbf{Programming Languages \& Frameworks:} Python, PyTorch, TensorFlow, Keras, Java
    \item \textbf{Data Science \& Developer Tools:} NumPy, Pandas, Matplotlib, W\&B, Git
    \item \textbf{Soft Skills \& Academic Leadership:} Teamwork, Leadership, Technical Communication, Mentorship, Problem Solving, Collaboration, Time Management
\end{itemize}
\end{section}

% \begin{section}{SKILLS}
%     \begin{itemize}
%         \item \textbf{Machine Learning \& Deep Learning:} Design and implementation of neural architectures using PyTorch, TensorFlow, and Keras; optimization techniques for training and evaluation
%         \item \textbf{Computer Vision \& Generative Models:} Expertise in diffusion models, text-to-image and image-to-text generation, multimodal learning
%         \item \textbf{Natural Language Processing:} Representation learning, BERT-based models, text classification
%         \item \textbf{Data Analysis \& Visualization:} Proficient in statistical analysis and experimental evaluation with Python, NumPy, Pandas, Matplotlib, Seaborn, and Weights \& Biases
%         \item \textbf{Programming \& Development:} Strong Python background; additional experience with Java, and basic web development
%         \item \textbf{Collaboration \& Tools:} GitHub, Slack, Discord for version control and research collaboration
%     \end{itemize}
% \end{section}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{section}{LICENSES \& CERTIFICATIONS}
% \begin{multicols}{2}
\begin{itemize}
% \item {\textbf{Deep Learning Specialization} - \href{https://www.coursera.org/account/accomplishments/specialization/certificate/LGYU3FW9F9AX}{Credential}} \newline DeepLearning.AI - Aug 2022\newline Instructor: Andrew Ng 

% \item {\textbf{Funds. of Reinforcement Learning} - \href{https://www.coursera.org/account/accomplishments/certificate/L2QGQYLFC8DL}{Credential}}
% \newline University of Alberta - Aug 2022 \newline Instructor: Martha and Adam White
% \item {\textbf{Crash Course on Python} -\href{https://www.coursera.org/account/accomplishments/certificate/V9RF53KNW4TS}{Credential}} \newline Google - Aug 2022

% \item {\textbf{Machine Learning Specialization} - \href{https://www.coursera.org/account/accomplishments/specialization/certificate/JFDSEZCH8ECY}{Credential}} \newline DeepLearning.AI - Sep 2022 \newline Instructor: Andrew Ng

\item {\textbf{IELTS} - \href{https://drive.google.com/file/d/1XfEYpe3-X4sc2bJJEsDmZZdFyORwvGaf/view?usp=drivesdk}{Certificate}}
  \newline IDP - Dec 2025, Overall: 7.5, Listening: 9, Reading: 7.0, Writing: 6.5, Speaking: 7.0
\end{itemize}
% \end{multicols}
\end{section}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\pagebreak
\begin{section}{REFERENCES}
\begin{subsectionnobullet}{Dr. Mohammad Hossein Rohban}{rohban@sharif.edu}{Sharif University of Technology}{\href{https://scholar.google.com/citations?user=pRyJ6FkAAAAJ&hl=en}{Google Scholar}}
    \item {Associate Professor of Computer Engineering, Sharif University of Technology, Tehran, Iran}
\end{subsectionnobullet}

\begin{subsectionnobullet}{Dr. Mohammad Amin Fazli}{fazli@sharif.edu}{Sharif University of Technology}{\href{https://scholar.google.com/citations?user=veo-8swAAAAJ&hl=en}{Google Scholar}}
    \item {Associate Professor of Computer Engineering, Sharif University of Technology, Tehran, Iran}
\end{subsectionnobullet}

\begin{subsectionnobullet}{Dr. Mahdieh Soleymani Baghshah}{soleymani@sharif.edu}{Sharif University of Technology}{\href{https://scholar.google.com/citations?user=S1U0KlgAAAAJ}{Google Scholar}}
    \item {Associate Professor of Computer Engineering, Sharif University of Technology, Tehran, Iran}
\end{subsectionnobullet}

\end{section}

\end{document}